---
title: "pi_curves_nls"
author: "Ariana S Huffmyer"
date: "3/18/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, message = FALSE, warning = FALSE)
```

```{r load_packages}
#Read in required libraries
library("devtools")
library("ggplot2")
library("segmented")
library("plotrix")
library("gridExtra")
library("lubridate")
library("chron")
library("plyr")
library("dplyr")
library("tidyr")
library("tidyverse")
library("broom")
library("ggpubr")
library("minpack.lm")
library("ggpmisc")

```


PLATE1
# Import data
```{r import_data}
Data <-read.csv("/Users/talimass/Library/Mobile Documents/com~apple~CloudDocs/Documents/Documents - MacBook Pro/GitHub/Reserch-Methods/Data/ROI_Padina_light dark.csv", header=T, sep=";", na.string="NA") #reads in the data files
Data <- Data[, c("Date", "Time", "PAR", "ETR1","ETR2","ETR3","ETR4","ETR5","ETR6","ETR7","ETR8","ETR9")]
# change format from wide to long
Data <- Data %>%  pivot_longer(., cols = starts_with("ETR"), names_to = "sample.ID")
Data$value <- na_if(Data$value, 0)
#need to Remove all data at PAR values above where ETR hits zero
Data$PAR <- as.numeric(Data$PAR)
colnames(Data)[5] ="ETR"

```


# View Data plots
```{r}
#Data <- Data %>%
#  subset(ETR<40)

Data %>%
ggplot(aes(x=PAR, y=ETR, color=sample.ID))+
  geom_point()+
  geom_line()+
  facet_wrap("sample.ID")+
  theme_bw()
  
#Data <- Data %>%
 #filter(!sample.ID=="ETR2"& !sample.ID=="ETR6")

Data %>%
ggplot(aes(x=PAR, y=ETR, color=sample.ID))+
  geom_point()+
  geom_line()+
  facet_wrap("sample.ID")+
  theme_bw()

```

```{r}
set.seed(123)
Data.PI <- Data %>% subset(PAR<650) 
curve.nlsPIC <- Data.PI %>% nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))
coef(curve.nlsPIC)
plot(ETR ~ PAR, data = Data.PI)
lines(0:900,
      predict(curve.nlsPIC,
              newdata = data.frame(PAR = 0:900)))
```
# Define PI curve function as a nonlinear Least Squares regression of a quadratic fit, test nls fit
Aquatic Photosynthesis, Falkowski   
Pmax = max photosynthesis (AKA Am from Bayesian script)  
alpha = quantum yeild (AKA AQY from Bayesian script)  
I/E = irradiance (AKA PAR from Bayesian script)  
Rd = dark respiration   

Using fixed initial values (keeping for reference):  
```{r}

# Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR13"))
# Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR16"))
# Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR19"))
# Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR2"))
# Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR7"))
# Data.PI <- Data.PI %>% subset(Spat.ID!=("ETR1"))

nls_data1 <- Data.PI %>%
group_by(sample.ID) %>%
nest(-sample.ID) %>%
mutate(model1 = map(data, ~
nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4)) %>%
tidy %>%
dplyr::select(term, estimate) %>%
spread(term, estimate))) %>%
unnest(model1) %>%
mutate(Ik = Am/AQY)%>%
mutate(Date = "20240523") %>%
mutate(Plate = "Plate1") %>%
mutate(sample.ID.PAM = paste0(Date,"_",Plate,"_",sample.ID)) 
write_csv(nls_data1, "/Users/talimass/Library/Mobile Documents/com~apple~CloudDocs/Documents/Documents - MacBook Pro/GitHub/Reserch-Methods/Output/course_pi_curve_pars_NLS_fixedparms.csv")
```

Plot curve over data points.  
```{r}
augmented <- Data.PI %>%
  filter(PAR <650) %>%
  nest(-sample.ID) %>% 
  mutate(
    fit = map(data, ~ nls(ETR ~ (Am*((AQY*PAR)/(sqrt(Am^2 + (AQY*PAR)^2)))-Rd), data=., start=list(Am=0.7,  AQY=0.001, Rd=.4))),
    augmented = map(fit, augment),
  ) %>% 
  unnest(augmented)

augmented$ID <-augmented$sample.ID
Aug <- augmented %>% separate(ID, c("Sp", "Num", "Type"))

#all colonies together
pdf("/Users/talimass/Library/Mobile Documents/com~apple~CloudDocs/Documents/Documents - MacBook Pro/GitHub/Reserch-Methods/Output/Plate1_PI_Curve_Fit_Plots.pdf")
PI.curves <- Aug %>%
ggplot(aes(x=PAR, y=ETR, color=sample.ID))+
  geom_point() + 
  geom_line(aes(y=.fitted, x=PAR,group=sample.ID))+
  theme_classic()+
          labs(x = expression(paste('PAR (', mu, "mol photons m"^-2, 's'^-1,")")),
               y = expression(paste("ETR")))+
  theme(legend.position = "top")
PI.curves
dev.off()

```
